Wikipedia Text Mining and Entropy Analysis

### 2018-12-17 wiki_entropy/wiki_clustering.Rmd
working on imputing missing WALS data

```{r clustering}
##read in googlesheet
wiki_gs <- gs_title("Wikipedia_relative10")
wkpd <- gs_read(wiki_gs) 
LANGUAGES <- wkpd$Language

wkpd <- wkpd %>% 
  as.data.frame() %>%
  column_to_rownames(var = "language")

@@

```{r WALS_features}
FEATURES <- c(1:144)
for (i in c(1:144)) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all WALS features in correct syntax

>>>>

```{r clustering}
##read in googlesheet
wiki_gs <- gs_title("Wikipedia_absolute")
wkpd <- gs_read(wiki_gs) 
LANGUAGES <- wkpd$Language

wkpd <- wkpd %>% 
  as.data.frame() %>%
  column_to_rownames(var = "Language")

@@

```{r WALS_imputation}
#taken from https://www.tutorialspoint.com/r/r_mean_median_mode.htm
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}

## imputation based on Gelman & Hill Chapter 25
# http://www.stat.columbia.edu/~gelman/arm/missing.pdf
random.imp <- function(a) {
  missed <- is.na(a)
  num_missed <- sum(missed)
  a.obs <- a[!missed]
  imputed <- a
  imputed[missed] <- base::sample(a.obs, num_missed, replace=TRUE)
  return(imputed)
}

impute <- function(a, a.impute) {
  ifelse(is.na(a), a.impute, a)
}

wf.sub <- wals.feature(c("1A", "2A", "3A", "4A"))

a1.mode <- getmode(wf.sub$`1A`[!is.na(wf.sub$`1A`)]) #gets the most common non-na value of column 1A

n.sims <- 10
for (s in 1:n.sims) {
  a1 <- wf.sub$`1A`
  a1[is.na(a1)] <- getmode(a1[!is.na(a1)])
  lm.1 <- glm(a1 ~ unlist(a2.imp, use.names = FALSE) + unlist(a2.imp, use.names = TRUE) + unlist(a2.imp, use.names = TRUE), family = binomial)
  pred.1 <- rnorm(n, predict(lm.1), sigma.hat(lm.1))
  a1.imp <- impute(wf.sub[c("1A")], pred.1)
}

```{r WALS_clustering}
FEATURES <- c(1:144)
for (i in c(1:144)) {
  FEATURES[i] <- paste(FEATURES[i], "A", sep = "")
} #get all WALS features in correct syntax
